Hybrid platforms and bargaining power

### 2024-05-09 src/paper/application.tex
Fix references

Next, let us consider the bargaining outcomes in this three-sided setting.
\Cref{sec:cooperative_game_two_sided} formally describes the corresponding cooperative game, and \cref{prop:profit_sharing_two_sided} establishes the resulting profit shares.
To summarize, the shares of the various players are as follows.
\begin{proposition}
    \label{prop:profit_sharing_two_sided}
    \begin{align*}
        \pi_P(N_P, N_F, N_C) &= \int_0^1 s \Pi(N_P, s N_F) \ds, \\
        \pi_F(N_P, N_F, N_C) &= \int_0^1 s^2 N_F \partial_2 \Pi(N_P, s N_F) \ds \\
        CS(N_P, N_F, N_C) &= \int_0^1 s \Pi(N_P, s N_F) \ds.
    \end{align*}
\end{proposition}

@@

\section{More general results}
\label{sec:more_general_results}

@@

This section presents a number of results that can be derived even in this rather abstract setting.
Let us start with a technical, but very useful result.
\begin{proposition}
    \label{prop:unique_equilibrium}
    Under the conditions in \cref{ass:single_crossing}, the equilibrium is unique if it exists.
\end{proposition}
The intuition behind this result is that \cref{ass:single_crossing} ensures that the total profits achieved by the fringe is either concave or hump-shaped.
Consequently, it has at most one crossing with the -- convex and increasing -- total entry cost function (for $n_F > 0$).
This particular shape (concave or hump-shaped) is also the main driver for the later results about the comparative statics of equilibrium profits and entry.

@@

\begin{proof}[Proof of \cref{prop:unique_equilibrium}]
    \Cref{lem:slope_at_eq} states that for any positive $N_F^*$ for which $\pi_F(N_P, N_F^*) - N_F I_F$, the partial derivative with respect to the number of fringe firms is negative.
    Now assume by contradiction that $\exists 0 < N_F^* < N_F^{**}$ such that $\pi_F(N_P, N_F^*) = I_F N_F^*$ and $\pi_F(N_P, N_F^{**}) = I_F N_F^{**}$.
    But then the mean value theorem implies that there is a $\bar{N}_F \in (N_F^*, N_F^{**})$ such that $\partial_F \pi_F(N_P, \bar{N}_F) = I_F$.
    This is a contradiction, as $\partial_F \pi_F(N_P, N_F) < I_F$ for all $N_F^* < N_F$.
\end{proof}

@@

\begin{proof}[Proof of \cref{lem:profit_assumptions_total_surplus}]
    To show this, I go through the same steps as in the proof of \cref{lem:profit_assumptions}.
    Consider the function
    \begin{align*}
        g(x) = \frac{sx}{1 + sx} + \log(1 + sx).
    \end{align*}
    Also, let us define
    \begin{align*}
        G(x) &= \int_0^1 s g(sx) \ds \\
        &= \frac{1}{x + 1}.
    \end{align*}
    Clearly, $G$ is a strictly concave function of $x$.

    Now let us consider $h(x) = N_C \mu g(N_P V_P + V_F x).$
    By \cref{lem:single_crossing_affine_transformation}, $H(x) = \int_0^1 s h'(sx) \ds$ is also strictly concave in $x$.\footnote{
        Technically, the lemma establishes concavity \emph{or} being monotone decreasing.
        It does not matter for this application, but it is easy to see that $H$ is indeed strictly concave.
    }
    Finally, notice that $H(x)$ is exactly the profit function of the fringe:
    \begin{align*}
        \pi_F(N_P, N_F, N_C) = \int_0^1 N_F h'(s N_F) \ds,
    \end{align*}
    and thus the lemma is proven.
\end{proof}

>>>>

Next, let us consider the bargaining outcomes in this three-sided setting.
\Cref{sec:cooperative_game_two_sided} formally describes the corresponding cooperative game, and \cref{prop:profit_sharing_two_sided} establishes the resulting profit shares.
To summarize, the shares of the various players are as follows.
\begin{proposition}
    \label{prop:three_way_shapley_value}
    \begin{align*}
        \pi_P(N_P, N_F, N_C) &= \int_0^1 s \Pi(N_P, s N_F) \ds, \\
        \pi_F(N_P, N_F, N_C) &= \int_0^1 s^2 N_F \partial_2 \Pi(N_P, s N_F) \ds \\
        CS(N_P, N_F, N_C) &= \int_0^1 s \Pi(N_P, s N_F) \ds.
    \end{align*}
\end{proposition}

@@

\section{More general results}
\label{sec:results_more_general}

@@

This section presents a number of results that can be derived even in this rather abstract setting.
Let us start with a technical, but very useful result.
\begin{proposition}
    \label{prop:unique_equilibrium_more_general}
    Under the conditions in \cref{ass:single_crossing}, the equilibrium is unique if it exists.
\end{proposition}
The intuition behind this result is that \cref{ass:single_crossing} ensures that the total profits achieved by the fringe is either concave or hump-shaped.
Consequently, it has at most one crossing with the -- convex and increasing -- total entry cost function (for $n_F > 0$).
This particular shape (concave or hump-shaped) is also the main driver for the later results about the comparative statics of equilibrium profits and entry.

@@

\begin{proof}[Proof of \cref{prop:unique_equilibrium_more_general}]
    \Cref{lem:slope_at_eq} states that for any positive $N_F^*$ for which $\pi_F(N_P, N_F^*) - N_F I_F$, the partial derivative with respect to the number of fringe firms is negative.
    Now assume by contradiction that $\exists 0 < N_F^* < N_F^{**}$ such that $\pi_F(N_P, N_F^*) = I_F N_F^*$ and $\pi_F(N_P, N_F^{**}) = I_F N_F^{**}$.
    But then the mean value theorem implies that there is a $\bar{N}_F \in (N_F^*, N_F^{**})$ such that $\partial_F \pi_F(N_P, \bar{N}_F) = I_F$.
    This is a contradiction, as $\partial_F \pi_F(N_P, N_F) < I_F$ for all $N_F^* < N_F$.
\end{proof}

@@
